### 2022-11-13 NSF2022/Description/backgroundv2.tex

\begin{wrapfigure}[]{l}{2.1in}
  \centering
  \includegraphics[width=1in]{figures/Background/Peanut/PeanutFEM.pdf}
  \includegraphics[width=1in]{figures/Background/Peanut/PeanutIE.pdf}
  \caption{\label{fig:fem_vs_bie} \footnotesize A finite element method
  ({\em left}) requires meshing the entire domain (typically into
  triangles), while a BIE ({\em right}) requires meshing only the
  boundary of the domain.}
\end{wrapfigure}

Computational methods to solve the PDEs~\eqref{eqn:stokes}
and~\eqref{eqn:phase} are challenging to develop because of
the complicated and unbounded domain.
This challenge is compounded when dense
suspensions are considered. Integral equations (IEs) offer an
alternative formulation of the PDEs that only require meshing the
boundary of the granules rather than all of $\Omega(t)$
(Figure~\ref{fig:fem_vs_bie}), and the automatically satisfy far field
conditions. Additional advantages of an discretizations of IE
formulations include high-order, or even spectral, accuracy and
well-conditioned linear system that can be solved iteratively with a
mesh-independent number of Krylov iterations such as the generalized
minimal residual method (GMRES). However, IEs have challenges: nearly
touching granules requires a quadrature rule for nearly-singular
integrals; their discretization results in dense matrices; and they
cannot immediately be applied to non-linear PDEs. The IE community,
including PI Quaife, has developed a variety of tools to address these
numerical challenges, and we discuss our planned approach in
Section~\ref{sec:specificaim2}.

>>>>

\begin{wrapfigure}[]{l}{2.1in}
  \centering
  \includegraphics[width=1in]{figures/Background/Peanut/PeanutFEM.pdf}
  \includegraphics[width=1in]{figures/Background/Peanut/PeanutIE.pdf}
  \caption{\label{fig:fem_vs_bie} \footnotesize A finite element method
  ({\em left}) requires meshing the entire domain (typically into
  triangles), while a BIE ({\em right}) requires meshing only the
  boundary of the domain.}
\end{wrapfigure}
Computational methods to solve the PDEs~\eqref{eqn:stokes}
and~\eqref{eqn:phase} are challenging to develop because of
the complicated and unbounded domain.
This challenge is compounded when dense
suspensions are considered. Integral equations (IEs) offer an
alternative formulation of the PDEs that only require meshing the
boundary of the granules rather than all of $\Omega(t)$
(Figure~\ref{fig:fem_vs_bie}), and the automatically satisfy far field
conditions. Additional advantages of an discretizations of IE
formulations include high-order, or even spectral, accuracy and
well-conditioned linear system that can be solved iteratively with a
mesh-independent number of Krylov iterations such as the generalized
minimal residual method (GMRES). However, IEs have challenges: nearly
touching granules requires a quadrature rule for nearly-singular
integrals; their discretization results in dense matrices; and they
cannot immediately be applied to non-linear PDEs. The IE community,
including PI Quaife, has developed a variety of tools to address these
numerical challenges, and we discuss our planned approach in
Section~\ref{sec:specificaim2}.
